First steps in synthetic algebraic geometry

### 2017-03-19 snippets/properties-of-a1.tex
A further property of A^1

\begin{prop}The following properties of~$\affl$, as seen from the internal
point of view of~$\Zar(S)$, are consequences of~$\affl$ being (a local ring and) synthetically
quasicoherent:
% Adjust paragraph below the proof if numbering changes.
% Proof of third and seventh property references first property by number.
\begin{enumerate}
\item $\affl$ is a field in the sense that any element which is not zero is
invertible: $\forall x\?\affl\_ \neg(x = 0) \Rightarrow \speak{$x$ \inv}$. More generally,
for any number~$n \geq 0$,
\begin{multline*}
  \qquad\qquad \forall x_1,\ldots,x_n\?\affl\_
  \neg(x_1 = 0 \wedge \cdots \wedge x_n = 0) \Longrightarrow \\
  (\speak{$x_1$ \inv} \vee \cdots \vee \speak{$x_n$ \inv}). \qquad\qquad
\end{multline*}
\item $\affl$ is not a reduced ring: $\neg \forall x\?\affl\_ (\bigvee_{n \geq
0} x^n = 0) \Rightarrow x = 0.$
\item Any element of $\affl$ which is not invertible is nilpotent.
\item Any function~$\affl \to \affl$ is given by a unique polynomial
in~$\affl[T]$.
\item $\affl$ is \emph{weakly algebraically closed}, in the following sense:
Any monic polynomial~$p \in \affl[T]$ of degree at least one does \notnot have
a zero.
\item $\affl$ is infinite in the following sense: For any number~$n \geq 0$
and any given elements~$x_1,\ldots,x_n \? \affl$, there is \notnot an element~$y$
which is distinct from all of the~$x_i$.
\item $\affl$ fulfills the conclusion of the Nullstellensatz:
Let~$f_1,\ldots,f_m \in \affl[X_1,\ldots,X_n]$ be polynomials without a common
zero in~$(\affl)^n$. Then there are polynomials~$g_1,\ldots,g_m \in
\affl[X_1,\ldots,X_n]$ such that~$\sum_i g_i f_i = 1$.
\end{enumerate}\end{prop}

@@

>>>>

The ring object~$\affl$ in the big Zariski topos enjoys several special
properties, some of which are unique in that they're only possible in an
intuitionistic context. The following proposition compiles a short list of such
properties. At least one of these, the field property, was already noticed in
the 1970s by Anders Kock~\cite{kock:univ-proj-geometry}.

\begin{prop}The following properties of~$\affl$, as seen from the internal
point of view of~$\Zar(S)$, are consequences of~$\affl$ being (a local ring and) synthetically
quasicoherent:
% Adjust paragraph below the proof if numbering changes.
% Proof of third and eigth property references first property by number.
\begin{enumerate}
\item $\affl$ is a field in the sense that any element which is not zero is
invertible: $\forall x\?\affl\_ \neg(x = 0) \Rightarrow \speak{$x$ \inv}$. More generally,
for any number~$n \geq 0$,
\begin{multline*}
  \qquad\qquad \forall x_1,\ldots,x_n\?\affl\_
  \neg(x_1 = 0 \wedge \cdots \wedge x_n = 0) \Longrightarrow \\
  (\speak{$x_1$ \inv} \vee \cdots \vee \speak{$x_n$ \inv}). \qquad\qquad
\end{multline*}
\item $\affl$ is not a reduced ring: $\neg \forall x\?\affl\_ (\bigvee_{n \geq
0} x^n = 0) \Rightarrow x = 0.$
\item Any element of $\affl$ which is not invertible is nilpotent.
\item An element of~$\affl$ is nilpotent if and only if it is \notnot zero.
\item Any function~$\affl \to \affl$ is given by a unique polynomial
in~$\affl[T]$.
\item $\affl$ is \emph{weakly algebraically closed}, in the following sense:
Any monic polynomial~$p \in \affl[T]$ of degree at least one does \notnot have
a zero.
\item $\affl$ is infinite in the following sense: For any number~$n \geq 0$
and any given elements~$x_1,\ldots,x_n \? \affl$, there is \notnot an element~$y$
which is distinct from all of the~$x_i$.
\item $\affl$ fulfills the conclusion of the Nullstellensatz:
Let~$f_1,\ldots,f_m \in \affl[X_1,\ldots,X_n]$ be polynomials without a common
zero in~$(\affl)^n$. Then there are polynomials~$g_1,\ldots,g_m \in
\affl[X_1,\ldots,X_n]$ such that~$\sum_i g_i f_i = 1$.
\end{enumerate}\end{prop}

@@

\item Follows from the first and third property and the observation that
nilpotent elements are not invertible (else~$1 = 0$ in contradiction to~$\affl$
being a local ring).
